 \documentclass[12pt,a4paper]{article}
\begin{document}
	\begin{titlepage}
		
	
		\centering
		\textbf{\Huge Experiment 1}
		
		\vspace{1.5cm}
		
		{\huge The strain gauge and its applications}
		
		\vspace{4cm}
		
		\textbf{\LARGE Sahand Sabour}
		
		\vspace{2cm}
		
		\textbf{\large EEE220}
		
		\vspace{0.5cm}
		
		{\large Instrumentation and Control System}
		
		\vspace{1.5cm}
		
		
		
		
		
		\textbf{\large Student ID}
		
		\vspace{0.5cm}
		
		{\large 1614650}
		
		\vfill
		
		{\itshape Xi'an Jiaotong Liverpool University}
		
	\end{titlepage}

	
	
	\section{Overview}

	My name is Sahand Sabour. I am an Iranian student currently studying the third year of undergraduate degree in Xi'an Jiaotong Liverpool University, majoring in Computer Science and Technology. 
	As an international student living in Suzhou, China, I tend to work hard in order to achieve the things I dream of. I like to think of myself as ambitious and driven. I am quite fond of accomplishing what is thought of as rather hard or impossible to accomplish. 
	
	\section{Education}
	
	I am currently in the second semester of the third year in the Computer Science and Technology undergraduate program in XJTLU. I have achieved excellent academic performance for both of my previous years in XJTLU. Moreover, I have successfully passed six out of twelve possible levels of Mandarin classes that are provided in XJTLU. 
	
	\section{Skills}
	\indent
	\subitem \textbf{LEADERSHIP}
	\vspace{0.25cm}
	\subitem{As a leader of a team, I fully acknowledge my responsibilities and endeavor to assign the given tasks to each of my teammates accordingly. I am not a fan of a serious workplace and I believe that in order to increase productivity, a great relationship between the members of the team has to be created initially. I tend to investigate the upcoming problems and challenges and would consequently consult the team for possible solutions.}
	\vspace{0.5cm}
	
	
	\subitem \textbf{TEAMWORK}
	\vspace{0.25cm}
	\subitem{As a member of a team, I feel responsible towards the tasks that are assigned to me and I always make sure to complete them on time in the best possible form. I tend to follow what the leader of the team guides us to do and I believe that sharing the same mentality for achieving the team’s objective is highly essential for cooperation. Furthermore, I tend to express my ideas clearly in order to contribute to the team. }
	\vspace{0.5cm}
	 
	 \subitem \textbf{COMMUNICATION}
	 \vspace{0.25cm}
	 \subitem{I think of myself as a rather outgoing person. It is not difficult for me to start a conversation, whether it’s with a friend or a stranger on the street. I am fascinated by what could be achieved with a simple conversation. I am intrigued with sharing my ideas and hearing creative and innovative ideas from others likewise. I believe having a conversation and/or a debate with a person is one of the best ways to discover your errors and weaknesses, as well as being one of the most effective methods of learning about an individual’s characteristics and behavior.}
	 \vspace{0.5cm}
	
	\subitem \textbf{PROGRAMMING}
	\vspace{0.25cm}
	\subitem{I am rather fluent in python, html and CSS. Furthermore, I have intermediate knowledge regarding JavaScript, JQUERY, Java, C++ and PHP. I have worked on many programming projects and am eager to work on more projects as time passes. As my major suggests, I am also fairly familiar with the field of electrical and electronic engineering and am also eager to learn and pursuit more in this field. }
	\vspace{0.5cm}
	
	\subitem \textbf{PRESENTATION}
	\vspace{0.25cm}
	\subitem{I have presented in several different occasions. I believe that I public speaking is one of the most important skills to attain in order to succeed. Hence, in my stay in China, I have attended many activities including a TEDx presentation in order to improve my presentation skills. I have done presentations in both English and Mandarin. }
	\vspace{0.5cm}
	
	\subitem \textbf{LANGUAGE}
	\vspace{0.25cm}
	\subitem{I am able to speak Farsi (Persian), English and Mandarin fluently.	
	}
	
	\section{Hobbies}
	I quite enjoy playing soccer on the weekends. It's a great opportunity to gather with friends, have a friendly chat and enjoy a sport enjoyed by many worldwide. I am also interested in reading mystery novels, watching comedy shows and consider listening to music as one of the most enjoyable things life has to offer. 
	Also, I like fishing too so I'm down if you wanna fish sometime;)
	
	
\end{document}